Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials

### 2023-01-19 code/data-wrangling.qmd
rearranged files

library(tidyverse)
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)

@@

mistie3 <- mistie3 %>%
  mutate(current.location.180 = case_when(
    location_d180 == "Acute - Hospital" ~ "Hospital",
    location_d180 == "Acute - ICU" ~ "Hospital",
    location_d180 == "Dead" ~ "Dead",
    location_d180 == "Home" ~ "Home",
    location_d180 == "Rehab" ~ "Rehabilitation",
    location_d180 == "LTCF" ~ "Skilled Nursing Facility",
    location_d180 == "Hospice" ~ "Hospice",
  ))

@@

```{r output = TRUE}
print(table1, showAllLevels = FALSE)

>>>>

library(tidyverse)
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
library(kableExtra)

@@

mistie3 <- mistie3 %>%
  mutate(current.location.180 = case_when(
    location_d180 == "Acute - Hospital" ~ "Hospital",
    location_d180 == "Acute - ICU" ~ "Hospital",
    location_d180 == "Dead" ~ "Dead",
    location_d180 == "Home" ~ "Home",
    location_d180 == "Rehab" ~ "Rehabilitation",
    location_d180 == "LTCF" ~ "Skilled Nursing Facility",library(tidyverse)
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)
library(readxl)
library(Hmisc)
    location_d180 == "Hospice" ~ "Hospice",
  ))

@@

```{r output = TRUE}
kbl(table1)
```
